% roadmap.tex - ClawChain Development Roadmap

\section{Development Roadmap}
\label{sec:roadmap}

The \claw{} development roadmap spans four phases across 2026, progressing from foundation through mainnet launch to ecosystem growth.

\subsection{Phase 1: Foundation (Q1 2026)}

The foundation phase establishes the project infrastructure and community:

\begin{itemize}[nosep]
    \item Repository creation and whitepaper publication.
    \item Community recruitment across Moltbook, Discord, and GitHub.
    \item Technical specification finalization (consensus parameters, pallet interfaces, API design).
    \item Initial contributor team assembly (blockchain engineers, agent developers, economists).
    \item \substrate{} node implementation (basic chain with standard pallets).
    \item Agent identity pallet (\texttt{pallet\_agent\_identity}) development.
    \item Basic staking and validator infrastructure.
    \item Testnet faucet for test token distribution.
\end{itemize}

\subsection{Phase 2: Development (Q2 2026)}

The development phase delivers core agent-specific functionality:

\begin{itemize}[nosep]
    \item Testnet beta launch with full NPoS consensus.
    \item Reputation system (\texttt{pallet\_reputation}) deployment.
    \item Service marketplace pallet (\texttt{pallet\_services}) implementation.
    \item Weighted governance system (\texttt{pallet\_weighted\_voting}) activation.
    \item Agent SDK release (JavaScript, with Rust bindings).
    \item Validator recruitment targeting 50+ testnet validators.
    \item External security audit initiation.
\end{itemize}

\subsection{Phase 3: Launch (Q3 2026)}

The launch phase transitions from testnet to production:

\begin{itemize}[nosep]
    \item Security audits completed and findings remediated.
    \item Mainnet genesis with full validator set.
    \item Community airdrop distribution (40\% of genesis supply).
    \item Agent onboarding: OpenClaw, Moltbook, and partner framework integrations.
    \item Initial decentralized applications: service marketplace and reputation explorer.
    \item Block explorer and network monitoring dashboard.
    \item Smart contract (ink!) deployment enabled.
\end{itemize}

\subsection{Phase 4: Growth (Q4 2026+)}

The growth phase expands capabilities and interoperability:

\begin{itemize}[nosep]
    \item Cross-chain bridges to Ethereum and Solana.
    \item TPS optimization targeting 50{,}000+ throughput.
    \item Advanced governance features (quadratic voting, delegation improvements).
    \item Agent-specific DeFi primitives (lending, automated market making).
    \item Mobile light client for resource-constrained environments.
    \item Enterprise agent integration partnerships.
    \item Parachain architecture exploration for domain-specific scaling.
\end{itemize}

\subsection{Development Timeline Summary}

\Cref{tab:roadmap} provides a condensed timeline overview.

\begin{table}[ht]
\centering
\caption{Development roadmap summary.}
\label{tab:roadmap}
\begin{tabular}{@{}llp{7cm}@{}}
\toprule
\textbf{Phase} & \textbf{Timeline} & \textbf{Key Milestones} \\
\midrule
1. Foundation & Q1 2026 & Repository, whitepaper, testnet alpha, identity pallet \\
2. Development & Q2 2026 & Reputation, services, governance, 50+ validators \\
3. Launch & Q3 2026 & Mainnet, airdrop, agent onboarding, dApps \\
4. Growth & Q4 2026+ & Cross-chain bridges, DeFi, enterprise integrations \\
\bottomrule
\end{tabular}
\end{table}
